%!TEX root = nml-base.tex
\phantomsection\addcontentsline{toc}{section}{References}%
\section*{References}%
\label{s:references}
% 
% Define heading of bibliography to be empty, since we already have a heading above the text.
\renewcommand{\refname}{}

\phantomsection\addcontentsline{toc}{subsection}{Normative References}
\subsection*{Normative References}
\begin{thebibliography}{10}
\vspace*{-3em}

\bibitem[URN-OGF-NETWORK]{gfd-urn-ogf-network}
Freek Dijkstra, and Jeroen van der Ham.
\newblock {A URN Namespace for Network Resources}.
\newblock GWD-I \emph{draft-gwdi-urn-ogf-network} (Work in Progress), September 2012.
\newblock URL \url{https://forge.ogf.org/sf/go/doc16260}.
% \newblock URL \url{http://www.ogf.org/documents/GFD.152.pdf}.

\bibitem[ISO 8601]{iso8601}
% No author
\newblock {Data elements and interchange formats -- Information interchange -- Representation of dates and times}.
\newblock ISO 8601:2004 (Third edition), December 2004.
\newblock Section 4.3.2 (a), Complete representations of a date and time. Calendar date in basic format.
\newblock URL \url{http://www.iso.org/iso/home/store/catalogue_ics/catalogue_detail_ics.htm?csnumber=40874}.

\bibitem[G.800]{g800}
% No author
\newblock {Unified functional architecture of transport networks}.
\newblock ITU-T Recommendation G.800, February 2012.
\newblock URL \url{http://www.itu.int/rec/T-REC-G.800/}.

\bibitem[RDF-XML]{rdfxml}
Dave Beckett (editor)
\newblock {RDF/XML Syntax Specification (Revised)}
\newblock {W3C Recommendation 10 February 2004}.
\newblock URL \url{http://www.w3.org/TR/rdf-syntax-grammar/}.

\bibitem[RFC 2119]{rfc2119}
Scott Bradner.
\newblock {Key words for use in RFCs to Indicate Requirement Levels}.
\newblock RFC 2119 (Best Current Practice), March 1997.
\newblock URL \url{http://tools.ietf.org/html/rfc2119}.

\bibitem[RFC 3492]{punycode}
A. Costello
\newblock {Punycode: A Bootstring encoding of Unicode for Internationalized Domain Names in Applications (IDNA)}
\newblock RFC 3492 (Standards Track), March 2003
\newblock URL \url{http://tools.ietf.org/html/rfc3492}.

\bibitem[RFC 3986]{rfc3986}
Tim Berners-Lee, Roy T. Fielding, and Larry Masinter.
\newblock {Uniform Resource Identifier (URI): Generic Syntax}
\newblock RFC 3986 (Standards Track), January 2005.
\newblock URL \url{http://tools.ietf.org/html/rfc3986}.

\bibitem[Unicode]{casefolding}
The Unicode Consortium.
\newblock The Unicode Standard, Version 6.2.0. 
\newblock Mountain View, CA, USA. November 2012. ISBN 978-1-936213-07-8
\newblock Section 5.18, Case Mappings. Paragraph about Caseless Matching.
\newblock Normative URL \url{http://www.unicode.org/versions/Unicode6.2.0/}
\newblock Informative URL \url{ftp://ftp.unicode.org/Public/UNIDATA/CaseFolding.txt}

\bibitem[UNLOCODE]{unlocode}
% No author
\newblock {United Nations Code for Trade and Transport Locations}
\newblock UN/LOCODE, revision 2012-01, September 2012.
\newblock URL \url{http://www.unece.org/cefact/locode/welcome.html}.

\bibitem[WGS84]{wgs84}
% No author
\newblock {Department of Defense World Geodetic System 1984, Its Definition and Relationships With Local Geodetic Systems}
\newblock NIMA Technical Report TR8350.2, Third Edition, June 2004
\newblock URL \url{http://earth-info.nga.mil/GandG/publications/tr8350.2/tr8350_2.html}.

\bibitem[XML]{xml}
Henry S. Thompson, David Beech, Murray Maloney and Noah Mendelsohn
\newblock {XML Schema Part 1: Structures Second Edition}
\newblock {W3C Recommendation 28 October 2004}.
\newblock URL \url{http://www.w3.org/TR/xmlschema-1/}.

\end{thebibliography}

\phantomsection\addcontentsline{toc}{subsection}{Informative References}
\subsection*{Informative References}

\begin{thebibliography}{10}
\vspace*{-3em}

\bibitem[Dijkstra13]{nml-experimental}
Freek Dijkstra, et al.
\newblock {Experimental Features for NML 1}.
\newblock Work in Progress.

\bibitem[GFD.165]{gfd.165}
Paola Grosso, Aaron Brown, Aur\'elien Cedeyn, Freek Dijkstra, Jeroen van der Ham, Anand Patil, Pascale Primet, Martin Swany, and Jason Zurawski.
\newblock {Network Topology Descriptions in Hybrid Networks}
\newblock GFD 165 (Informational), March 2010.
\newblock URL \url{http://www.ogf.org/documents/GFD.165.pdf}.

\bibitem[RFC 6350]{vcard}
Simon Perreault.
\newblock {vCard Format Specification}
\newblock RFC 6350 (Standards Track), August 2011.
\newblock URL \url{http://tools.ietf.org/html/rfc6350}.

\bibitem[RFC 6351]{xcard}
S. Perreault.
\newblock {xCard: vCard XML Representation}
\newblock RFC 6351 (Standards Track), August 2011.
\newblock URL \url{http://tools.ietf.org/html/rfc6351}.

\bibitem[RDFVCARD]{rdf-vcard}
 Harry Halpin, Renato Iannella, Brian Suda, Norman Walsh
\newblock Representing vCard Objects in RDF
\newblock W3C Member Submission 20 January 2010.
\newblock URL \url{http://www.w3.org/TR/vcard-rdf/}.


\end{thebibliography}
